{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
fixed spelling error in section title
first paragraph of section comparison
added \section's of the two approaches I will compare to

\section{Comparison with other aproaches/further work}
\label{sec:furtherwork}

>>>>

\section{Comparison with other approaches/further work}
\label{sec:furtherwork}
In this section I will first give a short overview of two other approaches and then
I will compare them with the approach presented before and draw a conclusion.

\subsection{Observational Determinism for Concurrent Program Security}
\subsection{Flexible Scheduler-Independent Security}
